Retrofitting Effect Handlers onto OCaml

### 2020-11-17 retro-concurrency.tex
edits

We consider well-behaved Multicore OCaml programs to resume their continuations
\emph{exactly once}. This can be enforced by installing a finaliser on every
captured continuation that |discontinue|s the continuation during finalisation
and ignores the result:
\begin{lstlisting}
Gc.finalise (fun k ->
  try ignore (discontinue k Unwind) with _ -> ()) k
\end{lstlisting}
However, Multicore OCaml does not enforce this behaviour in order to avoid the
costs associated with installing a finaliser every time a continuation is
captured.

>>>>

We consider well-behaved Multicore OCaml programs to resume their continuations
\emph{exactly once}. This can be enforced by installing a finaliser on every
captured continuation that calls |discontinue| on the continuation during finalisation
and ignores the result:
\begin{lstlisting}
Gc.finalise (fun k ->
  try ignore (discontinue k Unwind) with _ -> ()) k
\end{lstlisting}
However, Multicore OCaml does not enforce this behaviour in order to avoid the
costs associated with installing a finaliser every time a continuation is
captured.
